QPLIB: A Library of Quadratic Programming Instances

### 2017-02-08 format.tex
make it more clear that indices are 1-based and only summed up number of quadratic/linear terms in constraints is given

The data is in free format (blanks separate values), but must occur in
the order given here. Any blank lines, or lines starting with any of the
characters !, \% or \# are ignored. Each term in the first column of
Table~\ref{tab-qplib-format} denotes a required value. Any strings beyond
those required on a given line will be regarded as comments and ignored.
Real values may either by in decimal or exponential formats; for the latter,
the exponent may be preceded by either the character \texttt{D} or \texttt{E},
e.g. \texttt{12.56D+2} or \texttt{12.56E+2}.

@@

$n^{Q^i}$ & total number of nonzeros (integer) in lower triangles of
$Q^i$  & [2,4] \\

@@

& i, row and column indices (integers) and value (real) for
 each entry of $Q^{i}$ for every $i \in \Mcm$,  if $n^{Q^i}$,

@@

$n^{b^i}$ & total number of nonzeros  (integer) in $b^i$ for all $i \in \Mcm$ &

@@

$i$\; $j$\; $b^i_{j}$ & i and index (integers) and value (real)
for each nonzero entry of $b^i$ for every $i \in \Mcm$, if $n^{b} > 0$,

>>>>

The data is in free format (blanks separate values), but must occur in
the order given here. Any blank lines, or lines starting with any of the
characters !, \% or \# are ignored. Each term in the first column of
Table~\ref{tab-qplib-format} denotes a required value. Any strings beyond
those required on a given line will be regarded as comments and ignored.
Real values may either by in decimal or exponential formats; for the latter,
the exponent may be preceded by either the character \texttt{D} or \texttt{E},
e.g. \texttt{12.56D+2} or \texttt{12.56E+2}. Variable and constraint indices
are \textbf{1-based}.

@@

$\sum_{i\in\Mcm} n^{Q^i}$ & number of nonzeros (integer) in lower triangles of
$Q^i$, sum up over all $i\in\Mcm$  & [2,4] \\

@@

& $i$, row and column indices (integers) and value (real) for
 each entry of $Q^{i}$ for every $i \in \Mcm$,  if $n^{Q^i}>0$,

@@

$\sum_{i\in\Mcm} n^{b^i}$ & number of nonzeros (integer) in $b^i$, sum up over all $i \in \Mcm$ &

@@

$i$\; $j$\; $b^i_{j}$ & $i$ and index (integers) and value (real)
for each nonzero entry of $b^i$ for every $i \in \Mcm$, if $n^{b^i} > 0$,
